Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-16 main.tex
:pencil: Update contributions

\listfiles
\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usepgfplotslibrary{patchplots,groupplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\ctikzset{american}
\usetikzlibrary{arrows,calc,matrix,patterns,pgfplots.groupplots,plotmarks,positioning}

@@

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we introduce Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but smartly distributed to simultaneously encode backscatter message and assist primary transmission.
	% Instead of treating reflection as fully informative/random or fully auxiliary/deterministic,
	One can adjust node input distribution for flexible primary-backscatter tradeoff.
	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.

	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.

	\emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

@@

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

	\begin{subsection}{Decision Threshold}
		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.

>>>>

\listfiles
\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usepgfplotslibrary{patchplots,groupplots}
\usetikzlibrary{decorations.pathreplacing,calligraphy}
\usetikzlibrary{arrows,calc,matrix,plotmarks,patterns,positioning}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\ctikzset{american}
\usetikzlibrary{arrows,calc,matrix,patterns,pgfplots.groupplots,plotmarks,positioning}

@@

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at backscatter nodes and considered \gls{sic} from primary to backscatter link.
	% It thus requires non-coherent primary encoding at transmitters, and re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	It thus requires non-coherent encoding at the transmitter and re-encoding, precoding, and subtraction at the receiver.
	Besides, the advantage of \gls{sic} is questionable because 1) the primary and backscatter symbols are mixed by multiplication instead of superposition, and 2) the backscatter symbol period is typically much longer under physical constraints.
	% Motivated by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	Motivated by those, we propose the concept of Metascatter that adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{irs}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{irs}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metacatter is essentially an \gls{ambc} node.

	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter based on average received power, then models their reflection patterns and backscatter paths within equivalent channel for primary decoding.
	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.

	% \emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
	% When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
	% Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.

	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user. Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is sequentially updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by \gls{dp} and \gls{smawk} algorithm.

	% \emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	% For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	% For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	% However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

@@

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}

	% \begin{figure*}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.3\linewidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.35\linewidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.27\linewidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure*}

	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

	\begin{subsection}{Decision Threshold}
		\begin{figure}[!t]
			\centering
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/energy_distribution.tex}
			}
			\caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
		\end{figure}

		For a given tag input distribution $\{\boldsymbol{p}_k\}$, we can formulate an equivalent information source with augmented alphabet of tag input combination.
		This equivalent source transmits at the total backscatter rate, and the input distribution is given by $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$.
